---
title: "01_intro_real estate_2"
format: html
editor: visual
---

# 

```{r message=FALSE, warning=FALSE}
library(sf)
library(dplyr)
library(tidyr)
library(scales)
library(ggplot2)
library(stringr)
library(here)
library(ggrepel)

```

```{r}
# ==============================================================================
# Data Loading Section (Absolute Path Fix)
# ==============================================================================

# 1. 直接指定絕對路徑 (強制告訴 R 資料在哪裡)
# 注意：路徑中的反斜線 "\" 都要改成正斜線 "/"
project_root <- "C:/Users/ray12/PBAG2"

csv_dir <- file.path(project_root, "data", "lvr_landcsv114Q3")
shp_dir <- file.path(project_root, "data", "map")

# 再次檢查路徑是否正確 (會在 Console 印出結果)
cat("設定 CSV 路徑:", csv_dir, "\n")
cat("設定 Map 路徑:", shp_dir, "\n")

if (!dir.exists(csv_dir)) stop(paste("❌ 仍然找不到 CSV 資料夾 ->", csv_dir, "\n請檢查路徑拼字是否完全正確。"))
if (!dir.exists(shp_dir)) stop(paste("❌ 仍然找不到 Map 資料夾 ->", shp_dir))

# ------------------------------------------------------------------------------
# 2. 建立 real_estate_data 列表
# ------------------------------------------------------------------------------
library(readr)
library(sf)

real_estate_data <- list()

# 列出所有 CSV 檔案
csv_files <- list.files(csv_dir, pattern = "\\.csv$", full.names = TRUE)

if(length(csv_files) == 0) {
  stop("❌ 路徑正確，但在資料夾中找不到任何 .csv 檔案！請檢查資料夾內容。")
}

cat("✅ 找到", length(csv_files), "個 CSV 檔案，正在讀取...\n")

for (f in csv_files) {
  fname <- basename(f)
  # 讀取檔案，強制所有欄位為文字
  real_estate_data[[fname]] <- read_csv(f, col_types = cols(.default = "c"), show_col_types = FALSE)
}

# ------------------------------------------------------------------------------
# 3. 建立 map_data 列表
# ------------------------------------------------------------------------------
map_data <- list()
shp_name <- "TOWN_MOI_1140318.shp"
shp_path <- file.path(shp_dir, shp_name)

if (file.exists(shp_path)) {
  cat("✅ 正在讀取 Shapefile 地圖...\n")
  sf_obj <- st_read(shp_path, quiet = TRUE)
  map_data[[shp_name]] <- sf_obj
} else {
  stop(paste("❌ 找不到 Shapefile ->", shp_path))
}

cat("\n🎉 資料載入大成功！可以繼續執行後面的畫圖程式碼了。\n")


# Function to save plots
save_map_plot <- function(plot,
                      filename,
                      width = 13,
                      height = 8,
                      dpi = 300,
                      folder = "plots") {

  if (!dir.exists(folder)) {
    dir.create(folder, recursive = TRUE)
  }

  filepath <- file.path(folder, filename)

  ggsave(filepath,
         plot = plot,
         width = width,
         height = height,
         dpi = dpi)
}

```

# Translation Dictionary

```{r}
# Define District Name Mapping (Chinese -> English)
district_map <- c(
  # Hsinchu City
  "新竹市" = "Hsinchu City", 
  "東區" = "East Dist.",
  "北區" = "North Dist.",
  "香山區" = "Xiangshan Dist.",
  
  # Hsinchu County
  "竹北市" = "Zhubei City",
  "竹東鎮" = "Zhudong Township",
  "新埔鎮" = "Xinpu Township",
  "關西鎮" = "Guanxi Township",
  "湖口鄉" = "Hukou Township",
  "新豐鄉" = "Xinfeng Township",
  "芎林鄉" = "Qionglin Township",
  "橫山鄉" = "Hengshan Township",
  "北埔鄉" = "Beipu Township",
  "寶山鄉" = "Baoshan Township",
  "峨眉鄉" = "Emei Township",
  "尖石鄉" = "Jianshi Township",
  "五峰鄉" = "Wufeng Township",
  
  # Taipei City
  "中正區" = "Zhongzheng Dist.",
  "大同區" = "Datong Dist.",
  "中山區" = "Zhongshan Dist.",
  "松山區" = "Songshan Dist.",
  "大安區" = "Da'an Dist.",
  "萬華區" = "Wanhua Dist.",
  "信義區" = "Xinyi Dist.",
  "士林區" = "Shilin Dist.",
  "北投區" = "Beitou Dist.",
  "內湖區" = "Neihu Dist.",
  "南港區" = "Nangang Dist.",
  "文山區" = "Wenshan Dist."
)

# Function to translate names safely
translate_name <- function(names) {
  sapply(names, function(x) ifelse(x %in% names(district_map), district_map[x], x))
}

```

# Load Map Data

```{r}
# Load township-level shapefile
map_data_raw <- map_data[["TOWN_MOI_1140318.shp"]]

```

# Average Land Prices

## Hsinchu Region (City & County)

### Data Processing

```{r}
# 1. Load and Combine Data
hsinchu <- list("j_lvr_land_a.csv", "o_lvr_land_a.csv") %>%
  lapply(function(file) {
    real_estate_data[[file]] %>%
      {
        colnames(.) <- as.character(unlist(.[1, ]))
        .[-1, ]
      } %>%
      select(1, 13, 23) 
  }) %>%
  bind_rows()

# 2. Filter and Rename
hsinchu <- hsinchu %>%
  filter(`main use` %in% c("住家用", "住商用", "住工用")) %>%
  rename(TOWNNAME = `The villages and towns urban district`) %>%
  rename(LANDPRICE = `the unit price (NTD / square meter)`)

# 3. Calculate Average Price
hsinchu_ave_price <- hsinchu %>%
  group_by(TOWNNAME) %>%
  summarise(
    avg_price = mean(
      as.numeric(str_replace_all(LANDPRICE, ",", "")),
      na.rm = TRUE
    )
  )

# 4. Handle Hsinchu City Split
price_to_copy <- hsinchu_ave_price %>%
  filter(TOWNNAME == "新竹市") %>%
  pull(avg_price)

if(length(price_to_copy) > 0) {
    hsinchu_ave_price <- hsinchu_ave_price %>%
      add_row(
        TOWNNAME = c("北區", "香山區", "東區"),
        avg_price = rep(price_to_copy, 3)
      ) %>%
      filter(TOWNNAME != "新竹市")
}

# 5. Add English Names and Label Text
hsinchu_ave_price <- hsinchu_ave_price %>%
  mutate(
    TOWNNAME_ENG = translate_name(TOWNNAME),
    # Create label: "Name \n Price"
    LABEL_TEXT = paste0(TOWNNAME_ENG, "\n", comma(round(avg_price, 0)))
  )

print(head(hsinchu_ave_price))

```

### Visualization: Bar Plot

```{r}
# Create the bar plot object
p_hsinchu_bar <- ggplot(hsinchu_ave_price, aes(x = reorder(TOWNNAME_ENG, avg_price), y = avg_price)) +
  geom_col(fill = "steelblue") +
  
  # Add labels with commas (e.g., 350,000)
  geom_text(aes(label = comma(round(avg_price, 0))), 
            hjust = -0.1, 
            size = 3.5) +
  
  coord_flip() +
  
  # Y-axis formatting
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.15))) + # Add space for labels
  
  labs(
    x = "District / Township",
    y = "Average Unit Price (NTD / m²)",
    title = "Average Real Estate Unit Price: Hsinchu Region"
  ) +
  
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text = element_text(size = 11),
    panel.grid.major.y = element_blank() # Clean look
  )

# Print and Save
print(p_hsinchu_bar)
save_map_plot(p_hsinchu_bar, "hsinchu_bar_english.png")

```

### Map Integration

```{r}
hsinchu_map_data <- map_data_raw %>%
  filter(COUNTYNAME %in% c("新竹縣", "新竹市")) %>%
  select(TOWNNAME, geometry)

hsinchu_map_data <- hsinchu_map_data %>%
  left_join(hsinchu_ave_price, by = "TOWNNAME") %>%
  replace_na(list(avg_price = NA))

# Calculate centroids for ggrepel
# This creates X and Y coordinates for label placement
hsinchu_coords <- suppressWarnings(st_centroid(hsinchu_map_data)) %>%
  st_coordinates() %>%
  as.data.frame()

hsinchu_map_data <- bind_cols(hsinchu_map_data, hsinchu_coords)

```

### Visualization: Heatmap with Leader Lines

```{r}
hsinchu_map <- ggplot(hsinchu_map_data) +
  geom_sf(aes(fill = avg_price), color = "white", size = 0.2) +
  
  # Use ggrepel for non-overlapping labels with lines
  geom_text_repel(
    aes(x = X, y = Y, label = LABEL_TEXT),
    size = 3,
    fontface = "bold",
    color = "black",
    bg.color = "white", # White outline (halo) for readability
    bg.r = 0.15,
    min.segment.length = 0, # Always draw lines if moved
    segment.color = "grey50",
    force = 5, # Push labels away from each other
    box.padding = 0.5
  ) +
  
  scale_fill_gradient(low = "#ADD8E6", high = "#8B0000", 
                      na.value = "gray95", labels = comma) +
  labs(
    title = "Hsinchu Region Land Prices Map",
    subtitle = "Labels show: District / Unit Price (NTD/m²)",
    fill = "Price (NTD/m²)"
  ) +
  theme_minimal() +
  theme(axis.text = element_blank(), axis.ticks = element_blank(), panel.grid = element_blank())

hsinchu_map
save_map_plot(hsinchu_map, "hsinchu_map_english.png")

```

## Taipei City

### Data Processing

```{r}
# 1. Load Data
taipei <- ("a_lvr_land_a.csv") %>%
  lapply(function(file) {
    real_estate_data[[file]] %>%
      {
        colnames(.) <- as.character(unlist(.[1, ]))
        .[-1, ]
      } %>%
      select(1, 13, 23)
  }) %>%
  bind_rows()

# 2. Filter and Rename
taipei <- taipei %>%
  filter(`main use` %in% c("住家用", "住商用", "住工用")) %>%
  rename(TOWNNAME = `The villages and towns urban district`) %>%
  rename(LANDPRICE = `the unit price (NTD / square meter)`)

# 3. Calculate Average
taipei_ave_price <- taipei %>%
  group_by(TOWNNAME) %>%
  summarise(
    avg_price = mean(
      as.numeric(str_replace_all(LANDPRICE, ",", "")),
      na.rm = TRUE
    )
  )

# 4. Add English Names and Label Text
taipei_ave_price <- taipei_ave_price %>%
  mutate(
    TOWNNAME_ENG = translate_name(TOWNNAME),
    LABEL_TEXT = paste0(TOWNNAME_ENG, "\n", comma(round(avg_price, 0)))
  )

print(head(taipei_ave_price))

```

### Visualization: Bar Plot

```{r}
# Create the bar plot object
p_taipei_bar <- ggplot(taipei_ave_price, aes(x = reorder(TOWNNAME_ENG, avg_price), y = avg_price)) +
  geom_col(fill = "steelblue") +
  
  geom_text(aes(label = comma(round(avg_price, 0))), 
            hjust = -0.1, 
            size = 3.5) +
  
  coord_flip() +
  
  scale_y_continuous(labels = comma, expand = expansion(mult = c(0, 0.15))) +
  
  labs(
    x = "District",
    y = "Average Unit Price (NTD / m²)",
    title = "Average Real Estate Unit Price: Taipei City"
  ) +
  
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text = element_text(size = 11),
    panel.grid.major.y = element_blank()
  )

# Print and Save
print(p_taipei_bar)
save_map_plot(p_taipei_bar, "taipei_bar_english.png")

```

### Map Integration

```{r}
taipei_map_data <- map_data_raw %>%
  filter(COUNTYNAME %in% c("臺北市")) %>%
  select(TOWNNAME, geometry)

taipei_map_data <- taipei_map_data %>%
  left_join(taipei_ave_price, by = "TOWNNAME") %>%
  replace_na(list(avg_price = NA))

# Calculate centroids
taipei_coords <- suppressWarnings(st_centroid(taipei_map_data)) %>%
  st_coordinates() %>%
  as.data.frame()

taipei_map_data <- bind_cols(taipei_map_data, taipei_coords)

```

### Visualization: Heatmap with Leader Lines

```{r}
taipei_map <- ggplot(taipei_map_data) +
  geom_sf(aes(fill = avg_price), color = "white", size = 0.2) +
  
  geom_text_repel(
    aes(x = X, y = Y, label = LABEL_TEXT),
    size = 3,
    fontface = "bold",
    color = "black",
    bg.color = "white",
    bg.r = 0.15,
    min.segment.length = 0,
    segment.color = "grey50",
    force = 10, # Higher force for Taipei's dense districts
    box.padding = 0.4
  ) +
  
  scale_fill_gradient(low = "#ADD8E6", high = "#8B0000", 
                      na.value = "gray95", labels = comma) +
  labs(
    title = "Taipei City Land Prices Map",
    subtitle = "Labels show: District / Unit Price (NTD/m²)",
    fill = "Price (NTD/m²)"
  ) +
  theme_minimal() +
  theme(axis.text = element_blank(), axis.ticks = element_blank(), panel.grid = element_blank())

taipei_map
save_map_plot(taipei_map, "taipei_map_english.png")

```

# Export All Plots

Finally, we export all the generated visualizations to the `plots/` directory for use in the final report.

```{r}
# Export All Plots



# ==============================================================================
# Final Export Section
# Description: Saves all 4 plot objects created above to the 'plots' folder.
# ==============================================================================

# 1. Ensure output directory exists
output_dir <- here("plots")
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
  cat("Created output directory:", output_dir, "\n")
}

# 2. Save Hsinchu Plots
# (Bar Plot)
ggsave(file.path(output_dir, "hsinchu_bar_english.png"), 
       plot = p_hsinchu_bar, width = 12, height = 8, dpi = 300, bg = "white")

# (Heatmap Map)
ggsave(file.path(output_dir, "hsinchu_map_english.png"), 
       plot = hsinchu_map, width = 12, height = 8, dpi = 300, bg = "white")

# 3. Save Taipei Plots
# (Bar Plot)
ggsave(file.path(output_dir, "taipei_bar_english.png"), 
       plot = p_taipei_bar, width = 12, height = 8, dpi = 300, bg = "white")

# (Heatmap Map)
ggsave(file.path(output_dir, "taipei_map_english.png"), 
       plot = taipei_map, width = 12, height = 8, dpi = 300, bg = "white")

cat("\nSUCCESS: All 4 plots have been saved to:", output_dir, "\n")
```
