---
title: "Real_Estate_analysis"
format: 
  pdf:
    toc: true
---

# Libraries

```{r}
library(sf)
library(dplyr)
library(tidyr)
library(scales)
```

```{r}
suppressMessages(suppressWarnings(
  source(here::here("R", "load_data.R"))
))
```

```{r}
save_map_plot <- function(plot,
                      filename,
                      width = 13,
                      height = 8,
                      dpi = 300,
                      folder = "plots") {

  if (!dir.exists(folder)) {
    dir.create(folder, recursive = TRUE)
  }

  filepath <- file.path(folder, filename)

  ggsave(filepath,
         plot = plot,
         width = width,
         height = height,
         dpi = dpi)
}
```

# Load Map Data

```{r}
# Load township-level shapefile
map_data <- map_data[["TOWN_MOI_1140318.shp"]]
```

# Load Dataset

```{r}
# Look at the Metadata
manifest_list <- real_estate_data[["manifest.csv"]]
```
# Average Land Prices

## Hsinchu

In this section, we will try to analyze the elderly population data from Hsinchu City nd County and see its relationship with the average land prices.

```{r}
hsinchu <- list("j_lvr_land_a.csv", "o_lvr_land_a.csv") %>%
  lapply(function(file) {
    real_estate_data[[file]] %>%
      {
        colnames(.) <- as.character(unlist(.[1, ]))
        .[-1, ]
      } %>%
      select(1, 13, 23)
  }) %>%
  bind_rows()


hsinchu <- hsinchu %>%
  filter(`main use` %in% c("住家用", "住商用", "住工用")) %>%
  rename(TOWNNAME = `The villages and towns urban district`) %>%
  rename(LANDPRICE = `the unit price (NTD / square meter)`)


hsinchu_ave_price <- hsinchu %>%
  group_by(TOWNNAME) %>%
  summarise(
    avg_price = mean(
      as.numeric(str_replace_all(LANDPRICE, ",", "")),
      na.rm = TRUE
    )
  )

price_to_copy <- hsinchu_ave_price %>%
  filter(TOWNNAME == "新竹市") %>%
  pull(avg_price)

hsinchu_ave_price <- hsinchu_ave_price %>%
  add_row(
    TOWNNAME = c("北區", "香山區", "東區"),
    avg_price = price_to_copy
  ) %>%
  filter(TOWNNAME != "新竹市")
```

```{r}
hsinchu_map_data <- map_data %>%
  filter(COUNTYNAME %in% c("新竹縣", "新竹市")) %>%
  select(3, 4, 8)
```

```{r}
hsinchu_map_data <- hsinchu_map_data %>%
  left_join(hsinchu_ave_price, by = "TOWNNAME") %>%
  replace_na(list(avg_price = NA))
```

```{r}
# hsinchu_map <- ggplot(hsinchu_map_data) +
#                   geom_sf(aes(fill = avg_price), color = "white") +
#                   geom_sf_text(aes(label = TOWNNAME), size = 3, color = "black") +
#                   scale_fill_gradient(low = "lightblue", high = "darkred", na.value = "gray95") +
#                   labs(
#                     title = "Hsinchu Land Prices",
#                     fill = "Avg Price (NTD)"
#                   ) +
#                   theme_minimal()
# 
# hsinchu_map
# save_map_plot(hsinchu_map, "hsinchu_map_large.png")
```

## Taipei City

```{r}
taipei <- ("a_lvr_land_a.csv") %>%
  lapply(function(file) {
    real_estate_data[[file]] %>%
      {
        colnames(.) <- as.character(unlist(.[1, ]))
        .[-1, ]
      } %>%
      select(1, 13, 23)
  }) %>%
  bind_rows()


taipei <- taipei %>%
  filter(`main use` %in% c("住家用", "住商用", "住工用")) %>%
  rename(TOWNNAME = `The villages and towns urban district`) %>%
  rename(LANDPRICE = `the unit price (NTD / square meter)`)


taipei_ave_price <- taipei %>%
  group_by(TOWNNAME) %>%
  summarise(
    avg_price = mean(
      as.numeric(str_replace_all(LANDPRICE, ",", "")),
      na.rm = TRUE
    )
  )
```

```{r}
taipei_map_data <- map_data %>%
  filter(COUNTYNAME %in% c("臺北市")) %>%
  select(3, 4, 8)
```

```{r}
taipei_map_data <- taipei_map_data %>%
  left_join(taipei_ave_price, by = "TOWNNAME") %>%
  replace_na(list(avg_price = NA))
```

```{r}
# ggplot(taipei_ave_price, aes(x = reorder(TOWNNAME, avg_price), y = avg_price)) +
#   geom_col(fill = "steelblue") +
#   geom_text(aes(label = round(avg_price)), 
#             hjust = -0.1, 
#             size = 3.5) +
#   coord_flip() +
#   scale_y_continuous(labels = label_number(accuracy = 1)) +
#   labs(
#     x = "Town",
#     y = "Average Unit Price (NTD / square meter)",
#     title = "Average Unit Price by Taipei District"
#   ) +
#   theme_minimal() +
#   theme(plot.title = element_text(face = "bold"))
```

```{r}
# taipei_map <- ggplot(taipei_map_data) +
#                 geom_sf(aes(fill = avg_price), color = "white") +
#                 geom_sf_text(aes(label = TOWNNAME), size = 3, color = "black") +
#                 scale_fill_gradient(low = "lightblue", high = "darkred", na.value = "gray95") +
#                 labs(
#                   title = "Taipei District Land Prices",
#                   fill = "Avg Price (NTD)"
#                 ) +
#                 theme_minimal()
# 
# taipei_map
# save_map_plot(taipei_map, "taipei_map_large.png")
```

# Elderly Dependency Ratio and Average Lad Prices


## Hsinchu

```{r}
hsinchu_pop_data <- aging_data %>%
  filter(COUNTY %in% c("新竹縣", "新竹市")) %>%
  select(2, 4, 10) %>%
  mutate(A65UP_A15A64_RAT = as.integer(A65UP_A15A64_RAT)) %>%
  rename(TOWNNAME = TOWN)

hsinchu_pop_data
```

```{r}
hsinchu_map_data <- hsinchu_map_data %>%
  left_join(hsinchu_pop_data, by = "TOWNNAME")


hsinchu_map_data$avg_price <- as.numeric(hsinchu_map_data$avg_price)
hsinchu_map_data$A65UP_A15A64_RAT <- as.numeric(hsinchu_map_data$A65UP_A15A64_RAT)
```

### Bar Plot of Average Land Prices with Elderly Dependency Ratio as Second Scale

This plot demonstrates the comparison of the elderly dependency ratio vs average land prices per townships and districts in Hsinchu. This gives us an illustration of their relationship.

```{r}

# Compute scaling factor
scale_factor <- max(hsinchu_map_data$avg_price, na.rm = TRUE) / max(hsinchu_map_data$A65UP_A15A64_RAT, na.rm = TRUE)

ggplot(hsinchu_map_data, aes(x = TOWNNAME)) +
  geom_col(aes(y = avg_price), fill = "steelblue", width = 0.4, position = position_nudge(x = -0.2)) +
  geom_col(aes(y = A65UP_A15A64_RAT * scale_factor), fill = "orange", width = 0.4, position = position_nudge(x = 0.2)) +
  scale_y_continuous(
    name = "Average Land Price",
    sec.axis = sec_axis(~./scale_factor, name = "Hsinchu Elderly Dependency Ratio")
  ) +
  coord_flip() +
  theme_minimal()

```

### Hsinchu Linear Regression Model

```{r}
hsinchu_model <- lm(avg_price ~ A65UP_A15A64_RAT, data = hsinchu_map_data)
summary(hsinchu_model)

```

### Scatter Plot

The scatter plot shows us a better picture of the trend between the relationship of the elderly dependency ratio and the average land prices. In this case, we can see that the increase of the average land prices as an inverse relationship to the elderly dependency ratio.

```{r}

ggplot(hsinchu_map_data, aes(A65UP_A15A64_RAT, avg_price)) +
  geom_point(color = "steelblue", size = 3) +
  geom_smooth(method = "lm", color = "orange", se = FALSE) +
  labs(
    title = "Elderly Dependency Ratio and Average Land Price in Hsinchu",
    x = "Dependency Ratio",
    y = "Average Land Price (NTD / sqm)"
  ) +
  theme_minimal()

```

## Taipei City

We will do the same process to Taipei City

```{r}
taipei_pop_data <- aging_data %>%
  filter(COUNTY %in% c("臺北市")) %>%
  select(2, 4, 10) %>%
  mutate(A65UP_A15A64_RAT = as.integer(A65UP_A15A64_RAT)) %>%
  rename(TOWNNAME = TOWN)

taipei_pop_data
```

```{r}
taipei_map_data <- taipei_map_data %>%
  left_join(taipei_pop_data, by = "TOWNNAME")


taipei_map_data$avg_price <- as.numeric(taipei_map_data$avg_price)
taipei_map_data$A65UP_A15A64_RAT <- as.numeric(taipei_map_data$A65UP_A15A64_RAT)
```

### Bar Plot of Average Land Prices with Elderly Dependency Ratio as Second Scale

```{r}
# Compute scaling factor
scale_factor <- max(taipei_map_data$avg_price, na.rm = TRUE) / max(taipei_map_data$A65UP_A15A64_RAT, na.rm = TRUE)

ggplot(taipei_map_data, aes(x = TOWNNAME)) +
  geom_col(aes(y = avg_price), fill = "steelblue", width = 0.4, position = position_nudge(x = -0.2)) +
  geom_col(aes(y = A65UP_A15A64_RAT * scale_factor), fill = "orange", width = 0.4, position = position_nudge(x = 0.2)) +
  scale_y_continuous(
    name = "Average Land Price",
    sec.axis = sec_axis(~./scale_factor, name = "Taipei Elderly Dependency Ratio")
  ) +
  coord_flip() +
  theme_minimal()

```

### Taipei Linear Regression Model

```{r}
taipei_model <- lm(avg_price ~ A65UP_A15A64_RAT, data = taipei_map_data)
summary(taipei_model)

```

### Scatter Plot

In this scatter ploy, we can see an interesting trand where the increase of land prices has a directly proportional to the elderly dependency ratio.

```{r}

ggplot(taipei_map_data, aes(A65UP_A15A64_RAT, avg_price)) +
  geom_point(color = "steelblue", size = 3) +
  geom_smooth(method = "lm", color = "orange", se = FALSE) +
  labs(
    title = "Elderly Dependency Ratio and Average Land Price in Taipei",
    x = "Dependency Ratio",
    y = "Average Land Price (NTD / sqm)"
  ) +
  theme_minimal()

```
